Patterns in Knowledge Production: Political Ruptures and Imperial Dynamics Shaping Public Discourse in Sweden and Finland, 1640–1828

### 2017-11-20 inst/examples/20170201-manuscript.Rmd
Figs 5, 10, 15 fixed

```{r Figure_5prep, echo=FALSE, message=FALSE, warning=FALSE, fig.width=27, fig.height=14, fig.show="none", results="hide"}
rm(p)
rm(prow)
rm(legend_b)
pics <- list()
for (catalogue in na.omit(unique(df0$catalog))) {

@@

library(cowplot)
# arrange the three plots in a single row
prow <- plot_grid(
           pics[[1]] + theme(legend.position="none"),
           pics[[2]] + theme(legend.position="none"),
           pics[[3]] + theme(legend.position="none"),
           pics[[4]] + theme(legend.position="none"),	   
           align = 'vh',
           # labels = c("A", "B", "", ""),
	   # label_size = 25,	   
           hjust = -1,
           nrow = 2
           )

@@

@@

library(cowplot)
# arrange the three plots in a single row
prow <- plot_grid(
           pics[[1]] + theme(legend.position="none"),
           pics[[2]] + theme(legend.position="none"),
           pics[[3]] + theme(legend.position="none"),
           pics[[4]] + theme(legend.position="none"),	   
           align = 'vh',
           # labels = c("A", "B", "", ""),
	   # label_size = 25,	   
           hjust = -1,
           nrow = 2
           )

>>>>

```{r Figure_5prep, echo=FALSE, message=FALSE, warning=FALSE, fig.width=27, fig.height=14, fig.show="none", results="hide"}
rm(p)
rm(prow)
rm(legend_b)
pics <- list()

for (catalogue in na.omit(unique(df0$catalog))) {

@@

library(cowplot)
# arrange the three plots in a single row
prow <- plot_grid(
           pics[["Fennica-n"]] + theme(legend.position="none"),
           pics[["Fennica-paper"]] + theme(legend.position="none"),
           pics[["Kungliga-n"]] + theme(legend.position="none"),
           pics[["Kungliga-paper"]] + theme(legend.position="none"),
           align = 'vh',
           # labels = c("A", "B", "", ""),
	   # label_size = 25,	   
           hjust = -1,
           nrow = 2
           )

@@

# Translate
npub$publisher <- gsub("ja poika", "and son", npub$publisher)
npub$publisher <- gsub("Frenckellin leski", "Frenckell's widow", npub$publisher)

@@

library(cowplot)
# arrange the three plots in a single row
prow <- plot_grid(
           pics[["Fennica-Turku"]] + theme(legend.position="none"),
           pics[["Kungliga-Stockholm"]] + theme(legend.position="none"),
           pics[["Kungliga-Uppsala"]] + theme(legend.position="none"),
           pics[["Kungliga-Lund"]] + theme(legend.position="none"),	   	  
           align = 'vh',
           # labels = c("A", "B", "", ""),
	   # label_size = 25,	   
           hjust = -1,
           nrow = 2
           )
